When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-12-12 doc/agu_2017/vpd.tex
back to the conference

\begin{frame}{The question is, which effect dominates with an increase in VPD: plant response (decrease in ET) or atmospheric demand (increase in ET)?}
  \begin{itemize}
  \item Apriori intuition:
    \begin{itemize}
    \item Should be a function of plant type. e.g. plants that are evolved to conserve water will tend to reduce ET with increases in VPD.
    \item But the environment still matters: if the atmosphere dries enough  e.g. in very dry conditions the plants will not be able to conserve water, no matter how much they have evolved to do so.
    \end{itemize}
  \end{itemize}
\end{frame}

>>>>

\begin{frame}{The question is, which effect dominates with an increase in VPD: plant response (decrease in ET) or atmospheric demand (increase in ET)?}
  \begin{itemize}
  \item Prior intuition:
    \begin{itemize}
    \item Should be a function of plant type: plants that are evolved to conserve water will tend to reduce ET with increases in VPD.
    \item But the environment still matters: if the atmosphere dries enough plant water conservation strategies will max out and atmospheric demand drives increases in ET with increases in VPD.
    \end{itemize}
  \end{itemize}
\end{frame}
